COVID-19-Panel-Spain

### 2020-05-07 covid19env/data_processing/02-Data-Preprocessing-2.Rmd

Load climate data (ignore the humidity data in this file; it was a calculated variable):
```{r}
load("COVID-19-Datos_Climaticos_Spain-Extendido.RData")
```

@@

Prepare climatic factors:
```{r}
# Maximum temperature
TMax <- TMax %>% select(-ID, -provincia) %>%
  pivot_longer(starts_with("T"), 
               names_to = "Date",
               values_to = "Max_Temp") %>%
  mutate(Date = rep(seq(dmy("01-03-2020"), 
                        dmy("11-04-2020"), 
                        by = "days"), 
                    50))

# Minimum temperature
TMin <- TMin %>% select(-ID, -provincia) %>%
  pivot_longer(starts_with("T"), 
               names_to = "Date",
               values_to = "Min_Temp") %>%
  mutate(Date = rep(seq(dmy("01-03-2020"), 
                        dmy("11-04-2020"), 
                        by = "days"), 
                    50))

# Mean temperature
TMed <- TMed %>% select(-ID, -provincia) %>%
  pivot_longer(starts_with("T"), 
               names_to = "Date",
               values_to = "Mean_Temp") %>%
  mutate(Date = rep(seq(dmy("01-03-2020"), 
                        dmy("11-04-2020"), 
                        by = "days"), 
                    50))

# Hours of sunshine 
Sun <- Sun %>% select(-ID, -provincia) %>%
  pivot_longer(starts_with("S"), 
               names_to = "Date",
               values_to = "Sunshine_Hours") %>%
  mutate(Date = rep(seq(dmy("01-03-2020"), 
                        dmy("11-04-2020"), 
                        by = "days"), 
                    50))

# Precipitation 
Plu <- Plu %>% select(-ID, -provincia) %>%
  pivot_longer(c(starts_with("P")), 
               names_to = "Date",
               values_to = "Precipitation") %>%
  mutate(Date = rep(seq(dmy("01-03-2020"), 
                        dmy("11-04-2020"),
                        by = "days"), 
                    50)) %>%
  replace_na(list(Precipitation = 0)) # Replace two missing values in Malaga on 2020-03-01 and 2020-03-02

# Humidity 
Hum <- Hum %>% select(-provincia) %>%
  pivot_longer(c(starts_with("D")), 
               names_to = "Date",
               values_to = "Humidity") %>%
  mutate(Date = rep(seq(dmy("01-03-2020"), 
                        dmy("11-04-2020"),
                        by = "days"), 
                    50))
```

Join all climatic factors:
```{r}
climatic_vars <- TMax %>%
  left_join(TMin, by = c("ID_INE", "Date")) %>%
  left_join(TMed, by = c("ID_INE", "Date")) %>%
  left_join(Sun, by = c("ID_INE", "Date")) %>%
  left_join(Plu, by = c("ID_INE", "Date"))  %>%
  left_join(Hum, by = c("ID_INE", "Date"))
```

It is important to note that someone who is diagnosed on day "date" was likely infected between 2 and 12 days earlier. Therefore, the climatic variables need to be with respect to the likely time of contagion. For this reason, we calculate a lagged average using the variable from date-minus-12 to date-minus-5 days. These variables are called "lag8".
```{r}
# Lagged mean temperature: 8 day average
TMed_lag8 <- TMed %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Mean_Temp, 12) + 
                      lag(.x$Mean_Temp, 11)+ 
                      lag(.x$Mean_Temp, 10)+ 
                      lag(.x$Mean_Temp, 9)+ 
                      lag(.x$Mean_Temp, 8)+ 
                      lag(.x$Mean_Temp, 7)+ 
                      lag(.x$Mean_Temp, 6)+ 
                      lag(.x$Mean_Temp, 5))/8) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            Date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Mean_Temp_lag8 = value)

# Lagged sunshine hours: 8 day average
Sun_lag8 <- Sun %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Sunshine_Hours, 12) + 
                      lag(.x$Sunshine_Hours, 11)+ 
                      lag(.x$Sunshine_Hours, 10)+ 
                      lag(.x$Sunshine_Hours, 9)+ 
                      lag(.x$Sunshine_Hours, 8)+ 
                      lag(.x$Sunshine_Hours, 7)+ 
                      lag(.x$Sunshine_Hours, 6)+ 
                      lag(.x$Sunshine_Hours, 5))/8) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            Date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Sunshine_Hours_lag8 = value)

# Lagged precipitation: 8 day average
Plu_lag8 <- Plu %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Precipitation, 12) + 
                      lag(.x$Precipitation, 11)+ 
                      lag(.x$Precipitation, 10)+ 
                      lag(.x$Precipitation, 9)+ 
                      lag(.x$Precipitation, 8)+ 
                      lag(.x$Precipitation, 7)+ 
                      lag(.x$Precipitation, 6)+ 
                      lag(.x$Precipitation, 5))/8) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            Date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Precipitation_lag8 = value)

# Lagged humidity: 8 day average
Hum_lag8 <- Hum %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Humidity, 12) + 
                      lag(.x$Humidity, 11)+ 
                      lag(.x$Humidity, 10)+ 
                      lag(.x$Humidity, 9)+ 
                      lag(.x$Humidity, 8)+ 
                      lag(.x$Humidity, 7)+ 
                      lag(.x$Humidity, 6)+ 
                      lag(.x$Humidity, 5))/8) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            Date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Humidity_lag8 = value)
```

A variation of this is a lagged 11-day average, from date-minus-12 to date-minus-2 days. According to [this research](https://annals.org/aim/fullarticle/2762808/incubation-period-coronavirus-disease-2019-covid-19-from-publicly-reported) on the incubation period, this is the latency period of 95% of people who develop symptoms. Call this "lag11":
```{r}
# Lagged mean temperature: 8 day average
TMed_lag11 <- TMed %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Mean_Temp, 12) + 
                      lag(.x$Mean_Temp, 11) + 
                      lag(.x$Mean_Temp, 10) + 
                      lag(.x$Mean_Temp, 9) + 
                      lag(.x$Mean_Temp, 8) + 
                      lag(.x$Mean_Temp, 7) + 
                      lag(.x$Mean_Temp, 6) + 
                      lag(.x$Mean_Temp, 5)+ 
                      lag(.x$Mean_Temp, 4)+ 
                      lag(.x$Mean_Temp, 3)+ 
                      lag(.x$Mean_Temp, 2))/11) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            Date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Mean_Temp_lag11 = value)

# Lagged sunshine hours: 8 day average
Sun_lag11 <- Sun %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Sunshine_Hours, 12) + 
                      lag(.x$Sunshine_Hours, 11) + 
                      lag(.x$Sunshine_Hours, 10) + 
                      lag(.x$Sunshine_Hours, 9) + 
                      lag(.x$Sunshine_Hours, 8) + 
                      lag(.x$Sunshine_Hours, 7) + 
                      lag(.x$Sunshine_Hours, 6) + 
                      lag(.x$Sunshine_Hours, 5) + 
                      lag(.x$Sunshine_Hours, 4) + 
                      lag(.x$Sunshine_Hours, 3) + 
                      lag(.x$Sunshine_Hours, 2))/11) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            Date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Sunshine_Hours_lag11 = value)

# Lagged precipitation: 8 day average
Plu_lag11 <- Plu %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Precipitation, 12) + 
                      lag(.x$Precipitation, 11) + 
                      lag(.x$Precipitation, 10) + 
                      lag(.x$Precipitation, 9) + 
                      lag(.x$Precipitation, 8) + 
                      lag(.x$Precipitation, 7) + 
                      lag(.x$Precipitation, 6) + 
                      lag(.x$Precipitation, 5) + 
                      lag(.x$Precipitation, 4) + 
                      lag(.x$Precipitation, 3) + 
                      lag(.x$Precipitation, 2))/11) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            Date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Precipitation_lag11 = value)

# Lagged humidity: 8 day average
Hum_lag11 <- Hum %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Humidity, 12) + 
                      lag(.x$Humidity, 11) + 
                      lag(.x$Humidity, 10) + 
                      lag(.x$Humidity, 9) + 
                      lag(.x$Humidity, 8) + 
                      lag(.x$Humidity, 7) + 
                      lag(.x$Humidity, 6) + 
                      lag(.x$Humidity, 5) + 
                      lag(.x$Humidity, 4) + 
                      lag(.x$Humidity, 3) + 
                      lag(.x$Humidity, 2))/11) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            Date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Humidity_lag11 = value)
```

@@

Call this "lag11w":
```{r}
# Lagged mean temperature: 8 day average
TMed_lag11w <- TMed %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Mean_Temp, 12) * tweights$w[12] + 
                      lag(.x$Mean_Temp, 11) * tweights$w[11]+ 
                      lag(.x$Mean_Temp, 10) * tweights$w[10]+ 
                      lag(.x$Mean_Temp, 9) * tweights$w[9]+ 
                      lag(.x$Mean_Temp, 8) * tweights$w[8]+ 
                      lag(.x$Mean_Temp, 7) * tweights$w[7]+ 
                      lag(.x$Mean_Temp, 6) * tweights$w[6]+ 
                      lag(.x$Mean_Temp, 5) * tweights$w[5]+ 
                      lag(.x$Mean_Temp, 4) * tweights$w[4]+ 
                      lag(.x$Mean_Temp, 3) * tweights$w[3]+ 
                      lag(.x$Mean_Temp, 2) * tweights$w[2])) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            Date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Mean_Temp_lag11w = value)

# Lagged sunshine hours: 8 day average
Sun_lag11w <- Sun %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Sunshine_Hours, 12) * tweights$w[12] + 
                      lag(.x$Sunshine_Hours, 11) * tweights$w[11]+ 
                      lag(.x$Sunshine_Hours, 10) * tweights$w[10]+ 
                      lag(.x$Sunshine_Hours, 9) * tweights$w[9]+ 
                      lag(.x$Sunshine_Hours, 8) * tweights$w[8]+ 
                      lag(.x$Sunshine_Hours, 7) * tweights$w[7]+ 
                      lag(.x$Sunshine_Hours, 6) * tweights$w[6]+ 
                      lag(.x$Sunshine_Hours, 5) * tweights$w[5]+ 
                      lag(.x$Sunshine_Hours, 4) * tweights$w[4]+ 
                      lag(.x$Sunshine_Hours, 3) * tweights$w[3]+ 
                      lag(.x$Sunshine_Hours, 2) * tweights$w[2])) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            Date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Sunshine_Hours_lag11w = value)

# Lagged precipitation: 8 day average
Plu_lag11w <- Plu %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Precipitation, 12) * tweights$w[12] + 
                      lag(.x$Precipitation, 11) * tweights$w[11]+ 
                      lag(.x$Precipitation, 10) * tweights$w[10]+ 
                      lag(.x$Precipitation, 9) * tweights$w[9]+ 
                      lag(.x$Precipitation, 8) * tweights$w[8]+ 
                      lag(.x$Precipitation, 7) * tweights$w[7]+ 
                      lag(.x$Precipitation, 6) * tweights$w[6]+ 
                      lag(.x$Precipitation, 5) * tweights$w[5]+ 
                      lag(.x$Precipitation, 4) * tweights$w[4]+ 
                      lag(.x$Precipitation, 3) * tweights$w[3]+ 
                      lag(.x$Precipitation, 2) * tweights$w[2])) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            Date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Precipitation_lag11w = value)

# Lagged humidity: 8 day average
Hum_lag11w <- Hum %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Humidity, 12) * tweights$w[12] + 
                      lag(.x$Humidity, 11) * tweights$w[11]+ 
                      lag(.x$Humidity, 10) * tweights$w[10]+ 
                      lag(.x$Humidity, 9) * tweights$w[9]+ 
                      lag(.x$Humidity, 8) * tweights$w[8]+ 
                      lag(.x$Humidity, 7) * tweights$w[7]+ 
                      lag(.x$Humidity, 6) * tweights$w[6]+ 
                      lag(.x$Humidity, 5) * tweights$w[5]+ 
                      lag(.x$Humidity, 4) * tweights$w[4]+ 
                      lag(.x$Humidity, 3) * tweights$w[3]+ 
                      lag(.x$Humidity, 2) * tweights$w[2])) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            Date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Humidity_lag11w = value)
```

Join lagged variables to climatic factors:
```{r}
climatic_vars <- climatic_vars %>%
  left_join(TMed_lag8, by = c("ID_INE", "Date")) %>%
  left_join(Sun_lag8, by = c("ID_INE", "Date")) %>%
  left_join(Plu_lag8, by = c("ID_INE", "Date")) %>%
  left_join(Hum_lag8, by = c("ID_INE", "Date")) %>%
  left_join(TMed_lag11, by = c("ID_INE", "Date")) %>%
  left_join(Sun_lag11, by = c("ID_INE", "Date")) %>%
  left_join(Plu_lag11, by = c("ID_INE", "Date")) %>%
  left_join(Hum_lag11, by = c("ID_INE", "Date")) %>%
  left_join(TMed_lag11w, by = c("ID_INE", "Date")) %>%
  left_join(Sun_lag11w, by = c("ID_INE", "Date")) %>%
  left_join(Plu_lag11w, by = c("ID_INE", "Date")) %>%
  left_join(Hum_lag11w, by = c("ID_INE", "Date"))
```

@@

Join the dataframes:
```{r}
covid19_spain <- covid19_spain %>%
  full_join(climatic_vars, by = c("ID_INE", "Date"))
```

@@

## Plot two control variables Ratio Male/Female; Median_Age

Ratio of male to female in province:
```{r}
ggplot(data = provinces_spain) + 
  geom_sf(aes(fill = Male2Female)) + 
  scale_fill_distiller(palette = "Blues", direction = 1) + 
  theme_tufte()
```

Median age of population in province:
```{r}
ggplot(data = provinces_spain) + 
  geom_sf(aes(fill = Median_Age)) + 
  scale_fill_distiller(palette = "Blues", direction = 1) + 
  theme_tufte()
```

### Incidence progress

Plot the progression of the incidence of COVID-19 cases by province:
```{r}
p1 <- ggplot(data = covid19_spain %>%
               filter(Date == "2020-03-19") %>% 
         left_join(provinces_spain, by = "ID_INE") %>% 
         st_as_sf()) + 
  geom_sf(aes(fill = Incidence)) + 
  scale_fill_distiller(palette = "Reds", direction = 1) + 
  theme_tufte() +
  theme(axis.text = element_blank(),
        legend.position = "bottom") + 
  facet_wrap(~ Date, nrow = 3)

p2 <- ggplot(data = covid19_spain %>%
               filter(Date == "2020-03-28") %>% 
         left_join(provinces_spain, by = "ID_INE") %>% 
         st_as_sf()) + 
  geom_sf(aes(fill = Incidence)) + 
  scale_fill_distiller(palette = "Reds", direction = 1) + 
  theme_tufte() +
  theme(axis.text = element_blank(),
        legend.position = "bottom") + 
  facet_wrap(~ Date, nrow = 3)

p3 <- ggplot(data = covid19_spain %>%
               filter(Date == "2020-04-03") %>% 
         left_join(provinces_spain, by = "ID_INE") %>% 
         st_as_sf()) + 
  geom_sf(aes(fill = Incidence)) + 
  scale_fill_distiller(palette = "Reds", direction = 1) + 
  theme_tufte() +
  theme(axis.text = element_blank(),
        legend.position = "bottom") +
  facet_wrap(~ Date, nrow = 3)

gridExtra::grid.arrange(p1, p2, p3, ncol = 3)
```

@@

Filter missing records:
```{r}
covid19_spain <- covid19_spain %>%
  filter(!is.na(province)) %>% # Remove records that are missing data on the province
  filter(!is.na(Max_Temp)) # Remove records that are missing climatic variables

@@

Summary after cleaning:
```{r}
summary(covid19_spain)
```

@@

Save:
```{r}
# Dataframe
save(covid19_spain, file = "covid19_spain.RData", compress = "xz")

>>>>

Load climate data (This is the output of `01-Preprocess-meteo-data.Rmd`):
```{r}
load("meteo_data_province.RData")
```

@@

Arrange humidity data:
```{r}
# Humidity 
Hum <- Hum %>% select(-provincia) %>%
  pivot_longer(c(starts_with("D")), 
               names_to = "Date",
               values_to = "Humidity") %>%
  mutate(Date = rep(seq(dmy("01-03-2020"), 
                        dmy("11-04-2020"),
                        by = "days"), 
                    50))
```

Join all climatic factors:
```{r}
meteo_data_province <- meteo_data_province %>%
  left_join(Hum, by = c("ID_INE", "date" = "Date")) %>%
  rename(Max_Temp = MaxTemperature,
         Min_Temp = MinTemperature,
         Mean_Temp = MeanTemperature,
         Sunshine_Hours = SunshineHours) %>% 
  filter(date >= "2020-03-01" & date <= "2020-04-11")
```

It is important to note that someone who is diagnosed on day "date" was likely infected between 2 and 12 days earlier. Therefore, the climatic variables need to be with respect to the likely time of contagion. For this reason, we calculate a lagged average using the variable from date-minus-12 to date-minus-5 days. These variables are called "lag8".
```{r}
# Lagged mean temperature: 8 day average
TMed_lag8 <- meteo_data_province %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Mean_Temp, 12) + 
                      lag(.x$Mean_Temp, 11)+ 
                      lag(.x$Mean_Temp, 10)+ 
                      lag(.x$Mean_Temp, 9)+ 
                      lag(.x$Mean_Temp, 8)+ 
                      lag(.x$Mean_Temp, 7)+ 
                      lag(.x$Mean_Temp, 6)+ 
                      lag(.x$Mean_Temp, 5))/8) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Mean_Temp_lag8 = value)

# Lagged sunshine hours: 8 day average
Sun_lag8 <- meteo_data_province %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Sunshine_Hours, 12) + 
                      lag(.x$Sunshine_Hours, 11)+ 
                      lag(.x$Sunshine_Hours, 10)+ 
                      lag(.x$Sunshine_Hours, 9)+ 
                      lag(.x$Sunshine_Hours, 8)+ 
                      lag(.x$Sunshine_Hours, 7)+ 
                      lag(.x$Sunshine_Hours, 6)+ 
                      lag(.x$Sunshine_Hours, 5))/8) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Sunshine_Hours_lag8 = value)

# Lagged precipitation: 8 day average
Plu_lag8 <- meteo_data_province %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Precipitation, 12) + 
                      lag(.x$Precipitation, 11)+ 
                      lag(.x$Precipitation, 10)+ 
                      lag(.x$Precipitation, 9)+ 
                      lag(.x$Precipitation, 8)+ 
                      lag(.x$Precipitation, 7)+ 
                      lag(.x$Precipitation, 6)+ 
                      lag(.x$Precipitation, 5))/8) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Precipitation_lag8 = value)

# Lagged humidity: 8 day average
Hum_lag8 <- meteo_data_province %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Humidity, 12) + 
                      lag(.x$Humidity, 11)+ 
                      lag(.x$Humidity, 10)+ 
                      lag(.x$Humidity, 9)+ 
                      lag(.x$Humidity, 8)+ 
                      lag(.x$Humidity, 7)+ 
                      lag(.x$Humidity, 6)+ 
                      lag(.x$Humidity, 5))/8) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Humidity_lag8 = value)
```

A variation of this is a lagged 11-day average, from date-minus-12 to date-minus-2 days. According to [this research](https://annals.org/aim/fullarticle/2762808/incubation-period-coronavirus-disease-2019-covid-19-from-publicly-reported) on the incubation period, this is the latency period of 95% of people who develop symptoms. Call this "lag11":
```{r}
# Lagged mean temperature: 8 day average
TMed_lag11 <- meteo_data_province %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Mean_Temp, 12) + 
                      lag(.x$Mean_Temp, 11) + 
                      lag(.x$Mean_Temp, 10) + 
                      lag(.x$Mean_Temp, 9) + 
                      lag(.x$Mean_Temp, 8) + 
                      lag(.x$Mean_Temp, 7) + 
                      lag(.x$Mean_Temp, 6) + 
                      lag(.x$Mean_Temp, 5)+ 
                      lag(.x$Mean_Temp, 4)+ 
                      lag(.x$Mean_Temp, 3)+ 
                      lag(.x$Mean_Temp, 2))/11) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Mean_Temp_lag11 = value)

# Lagged sunshine hours: 8 day average
Sun_lag11 <- meteo_data_province %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Sunshine_Hours, 12) + 
                      lag(.x$Sunshine_Hours, 11) + 
                      lag(.x$Sunshine_Hours, 10) + 
                      lag(.x$Sunshine_Hours, 9) + 
                      lag(.x$Sunshine_Hours, 8) + 
                      lag(.x$Sunshine_Hours, 7) + 
                      lag(.x$Sunshine_Hours, 6) + 
                      lag(.x$Sunshine_Hours, 5) + 
                      lag(.x$Sunshine_Hours, 4) + 
                      lag(.x$Sunshine_Hours, 3) + 
                      lag(.x$Sunshine_Hours, 2))/11) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Sunshine_Hours_lag11 = value)

# Lagged precipitation: 8 day average
Plu_lag11 <- meteo_data_province %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Precipitation, 12) + 
                      lag(.x$Precipitation, 11) + 
                      lag(.x$Precipitation, 10) + 
                      lag(.x$Precipitation, 9) + 
                      lag(.x$Precipitation, 8) + 
                      lag(.x$Precipitation, 7) + 
                      lag(.x$Precipitation, 6) + 
                      lag(.x$Precipitation, 5) + 
                      lag(.x$Precipitation, 4) + 
                      lag(.x$Precipitation, 3) + 
                      lag(.x$Precipitation, 2))/11) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Precipitation_lag11 = value)

# Lagged humidity: 8 day average
Hum_lag11 <- meteo_data_province %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Humidity, 12) + 
                      lag(.x$Humidity, 11) + 
                      lag(.x$Humidity, 10) + 
                      lag(.x$Humidity, 9) + 
                      lag(.x$Humidity, 8) + 
                      lag(.x$Humidity, 7) + 
                      lag(.x$Humidity, 6) + 
                      lag(.x$Humidity, 5) + 
                      lag(.x$Humidity, 4) + 
                      lag(.x$Humidity, 3) + 
                      lag(.x$Humidity, 2))/11) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Humidity_lag11 = value)
```

@@

Call this "lag11w":
```{r}
# Lagged mean temperature: 8 day average
TMed_lag11w <- meteo_data_province %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Mean_Temp, 12) * tweights$w[12] + 
                      lag(.x$Mean_Temp, 11) * tweights$w[11]+ 
                      lag(.x$Mean_Temp, 10) * tweights$w[10]+ 
                      lag(.x$Mean_Temp, 9) * tweights$w[9]+ 
                      lag(.x$Mean_Temp, 8) * tweights$w[8]+ 
                      lag(.x$Mean_Temp, 7) * tweights$w[7]+ 
                      lag(.x$Mean_Temp, 6) * tweights$w[6]+ 
                      lag(.x$Mean_Temp, 5) * tweights$w[5]+ 
                      lag(.x$Mean_Temp, 4) * tweights$w[4]+ 
                      lag(.x$Mean_Temp, 3) * tweights$w[3]+ 
                      lag(.x$Mean_Temp, 2) * tweights$w[2])) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Mean_Temp_lag11w = value)

# Lagged sunshine hours: 8 day average
Sun_lag11w <- meteo_data_province %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Sunshine_Hours, 12) * tweights$w[12] + 
                      lag(.x$Sunshine_Hours, 11) * tweights$w[11]+ 
                      lag(.x$Sunshine_Hours, 10) * tweights$w[10]+ 
                      lag(.x$Sunshine_Hours, 9) * tweights$w[9]+ 
                      lag(.x$Sunshine_Hours, 8) * tweights$w[8]+ 
                      lag(.x$Sunshine_Hours, 7) * tweights$w[7]+ 
                      lag(.x$Sunshine_Hours, 6) * tweights$w[6]+ 
                      lag(.x$Sunshine_Hours, 5) * tweights$w[5]+ 
                      lag(.x$Sunshine_Hours, 4) * tweights$w[4]+ 
                      lag(.x$Sunshine_Hours, 3) * tweights$w[3]+ 
                      lag(.x$Sunshine_Hours, 2) * tweights$w[2])) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Sunshine_Hours_lag11w = value)

# Lagged precipitation: 8 day average
Plu_lag11w <- meteo_data_province %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Precipitation, 12) * tweights$w[12] + 
                      lag(.x$Precipitation, 11) * tweights$w[11]+ 
                      lag(.x$Precipitation, 10) * tweights$w[10]+ 
                      lag(.x$Precipitation, 9) * tweights$w[9]+ 
                      lag(.x$Precipitation, 8) * tweights$w[8]+ 
                      lag(.x$Precipitation, 7) * tweights$w[7]+ 
                      lag(.x$Precipitation, 6) * tweights$w[6]+ 
                      lag(.x$Precipitation, 5) * tweights$w[5]+ 
                      lag(.x$Precipitation, 4) * tweights$w[4]+ 
                      lag(.x$Precipitation, 3) * tweights$w[3]+ 
                      lag(.x$Precipitation, 2) * tweights$w[2])) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Precipitation_lag11w = value)

# Lagged humidity: 8 day average
Hum_lag11w <- meteo_data_province %>% 
  group_by(ID_INE) %>%
  group_modify(~ {((lag(.x$Humidity, 12) * tweights$w[12] + 
                      lag(.x$Humidity, 11) * tweights$w[11]+ 
                      lag(.x$Humidity, 10) * tweights$w[10]+ 
                      lag(.x$Humidity, 9) * tweights$w[9]+ 
                      lag(.x$Humidity, 8) * tweights$w[8]+ 
                      lag(.x$Humidity, 7) * tweights$w[7]+ 
                      lag(.x$Humidity, 6) * tweights$w[6]+ 
                      lag(.x$Humidity, 5) * tweights$w[5]+ 
                      lag(.x$Humidity, 4) * tweights$w[4]+ 
                      lag(.x$Humidity, 3) * tweights$w[3]+ 
                      lag(.x$Humidity, 2) * tweights$w[2])) %>%
      enframe()}) %>%
  ungroup() %>%
  transmute(ID_INE, 
            date = rep(seq(dmy("01-03-2020"),
                           dmy("11-04-2020"), 
                           by = "days"), 
                       50), 
            Humidity_lag11w = value)
```

Join lagged variables to climatic factors:
```{r}
meteo_data_province <- meteo_data_province %>%
  left_join(TMed_lag8, by = c("ID_INE", "date")) %>%
  left_join(Sun_lag8, by = c("ID_INE", "date")) %>%
  left_join(Plu_lag8, by = c("ID_INE", "date")) %>%
  left_join(Hum_lag8, by = c("ID_INE", "date")) %>%
  left_join(TMed_lag11, by = c("ID_INE", "date")) %>%
  left_join(Sun_lag11, by = c("ID_INE", "date")) %>%
  left_join(Plu_lag11, by = c("ID_INE", "date")) %>%
  left_join(Hum_lag11, by = c("ID_INE", "date")) %>%
  left_join(TMed_lag11w, by = c("ID_INE", "date")) %>%
  left_join(Sun_lag11w, by = c("ID_INE", "date")) %>%
  left_join(Plu_lag11w, by = c("ID_INE", "date")) %>%
  left_join(Hum_lag11w, by = c("ID_INE", "date"))
```

@@

Join the dataframes:
```{r}
covid19_spain <- covid19_spain %>%
  full_join(meteo_data_province, by = c("ID_INE", "Date" = "date"))
```

@@

@@

Filter missing records:
```{r}
covid19_spain_2 <- covid19_spain %>%
  filter(!is.na(province)) %>% # Remove records that are missing data on the province
  filter(!is.na(Mean_Temp)) # Remove records that are missing climatic variables

@@

Summary after cleaning:
```{r}
summary(covid19_spain_2)
```

@@

Save:
```{r}
# Dataframe
save(covid19_spain_2, file = "covid19_spain_2.RData", compress = "xz")
